Composition-climate paper

### 2015-07-14 Composition_Ecology.Rmd
Added new run with PDF and DOCX versions.  Don't have a good change history for the Rmd, something's wonky with RStudio.

---
title: "Composition-climate paper"
author: "Simon Goring *et al*."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document:
    fig_width: 6
    fig_height: 6
  md_document:
    variant: markdown_github
  pdf_document:
    pandoc_args: "-V geometry:vmargin=1in -V geometry:hmargin=1in"
pandoc_args: "-H margins.sty"
bibliography: goringetal_references.bib
csl: ecology.csl
---

>>>>

---
title: "Composition-climate paper"
author: "Simon Goring *et al*."
date: '`r format(Sys.time(), ''%d %B, %Y'')`'
output:
  pdf_document:
    pandoc_args: -V geometry:vmargin=1in -V geometry:hmargin=1in
  md_document:
    variant: markdown_github
  word_document:
    fig_height: 6
    fig_width: 6
csl: ecology.csl
pandoc_args: -H margins.sty
bibliography: goringetal_references.bib
---
